[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-09 README/getting_started_guide.tex
Added README.md to the repository
minor typos; moved the note aboutchanges in the experiments

Our artifact, dubbed Hybrid Resource-Aware ML (RaML), is a program analysis tool
that takes in an OCaml program and infers its worst-case polynomial cost bound
using the technique Hybrid AARA described in the paper.

@@

Load and run the Docker image as follows:
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
$ docker run --name hybrid_aara -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
%
Throughout this document, any command line starting with \texttt{\#} is executed
inside the Docker container, and any command line starting with \texttt{\$} is
executed in your local machine's terminal.

@@

>>>>

Our artifact, dubbed Hybrid Resource-Aware ML (Hybrid RaML), is a program analysis tool
that takes in an OCaml program and infers its worst-case polynomial cost bound
using the technique Hybrid AARA described in the paper.

@@

Load and run the Docker image as follows:
\begin{verbatim}
$ docker load --input hybrid_aara.tar.gz
$ docker run --name hybrid_aara -it --rm hybrid_aara
root@fca41f6f696d:/home/hybrid_aara/benchmark_suite/playground#
\end{verbatim}
%
It creates a Docker conainer (i.e., a runnable instance of the Docker image) and
starts a shell inside the container.
%
Throughout this document, any command line starting with \texttt{\#} is executed
inside the Docker container, and any command line starting with \texttt{\$} is
executed in your local machine's terminal.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "README"
%%% End:

### 2024-03-09 README/step_by_step_instructions.tex
minor typos; moved the note aboutchanges in the experiments

\subsection{Display Experiment Results}
\label{sec:display experiment results}

In this section, we demonstrate how to produce tables and plots in the paper
from the experiment results that are stored in each benchmark's \texttt{bin}
directory.
%
In the Docker container, the \texttt{bin} directory of each benchmark already
contains the experimental results that we reported in the paper.
%
We will demonstrate how to generate the experimental results from scratch in
\cref{sec:generate experiment results}.

The tables and plots produced by the artifact are different from the ones in the
submitted version of the paper.
%
This is because, since the submission, we have adjusted the hyperparameters for
\BayesWC{} and \BayesPC{} in order to an automatic procedure for choosing
hyperparameters.
%
The updated experiments results still preserve our key claims in Section~7 of
the paper.
%
The updated version of the paper accompanies the artifact.

@@

\subsection{Generate Experiment Results}
\label{sec:generate experiment results}

@@

To view the updated tables and plots of the new experiment results, follow the
steps in \cref{sec:display experiment results}.
%
The experiment results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
after rerunning the experiments may look different from the tables and plots
reported in the updated version of the paper.
%
This is because \BayesWC{} and \BayesPC{} run sampling-based Bayesian inference
algorithms that are stochastic.
%
Nonetheless, there should not be any significant deviation.

>>>>

\subsection{Display Experimental Results}
\label{sec:display experiment results}

In this section, we demonstrate how to produce tables and plots in the paper
from the experimental results that are stored in each benchmark's \texttt{bin}
directory.
%
In the Docker container, the \texttt{bin} directory of each benchmark already
contains the experimental results that we reported in the paper.
%
We will demonstrate how to generate the experimental results from scratch in
\cref{sec:generate experiment results}.

@@

\subsection{Generate Experimental Results}
\label{sec:generate experiment results}

@@

To view the updated tables and plots of the new experimental results, follow the
steps in \cref{sec:display experiment results}.
%
The experimental results for (Data-Driven and Hybrid) \BayesWC{} and \BayesPC{}
after rerunning the experiments may look different from the tables and plots
reported in the updated version of the paper.
%
This is because \BayesWC{} and \BayesPC{} run sampling-based Bayesian inference
algorithms that are stochastic.
%
Nonetheless, there should not be any significant deviation.

### 2024-03-09 README/what_is_included.tex
typo
minor typos; moved the note aboutchanges in the experiments

From Zenodo, you should obtain the following items:
\begin{itemize}
  \item This \texttt{README.pdf} document
  \item Archived and compressed Docker image \texttt{hybrid\_aara.tar.gz}
  \item Update version of the paper \texttt{paper.pdf}.
\end{itemize}

>>>>

From Zenodo, you should obtain the following items:
\begin{itemize}
  \item This \texttt{README.pdf} document
  \item Archived and compressed Docker image \texttt{hybrid\_aara.tar.gz}
  \item Updated version of the paper \texttt{paper.pdf}.
\end{itemize}

\emph{\textbf{Note:} The tables and plots produced by the artifact are
  slightly different from the ones in the submitted version of the
  paper.
%
  This is because, since the submission, we have adjusted the
  hyperparameters for \BayesWC{} and \BayesPC{} using an automatic
  procedure for choosing hyperparameters.
%
  The updated experiments results still preserve all key findings in
  Section~7 of the paper.
%
  The updated version of the paper accompanies the artifact.}
